 ---
title: "STAT423-Project-Code"
output: html_document
date: "2023-04-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in Survey Data
```{r}
library(readr)
survey.df <- read_csv("/.....file-path-to.../STAT423-SurveyData.csv") #reads our survey csv file into a dataframe
survey.df #view dataframe
```
We will calculate SRS without replacement, why? because our observations are selected randomly, and once an observation is selected it cant be selected again. 

As Q4-Q11 columns contain numerical values, we will calculate the sample mean $\bar{X}$ for each column using R

Q4 Sample Mean: $\bar{X} = 4.72$ 

```{r}
mean(survey.df$Q4, data=survey.df)
```

Q5 Sample Mean: $\bar{X} = 3.64$ 

```{r}
mean(survey.df$Q5, data=survey.df)
```

Q4&5 Sample Mean: $\bar{X} = 15.94$ 

```{r}
mean(survey.df$Q4and5, data=survey.df)
```


Q6 Sample Mean: $\bar{X} = 2.9$ 

```{r}
mean(survey.df$Q6, data=survey.df)
```
Q7 Sample Mean: $\bar{X} = 3.308$ 

```{r}
mean(survey.df$Q7, data=survey.df)
```

Q8 Sample Mean: $\bar{X} = 1.82$ 

```{r}
mean(survey.df$Q8, data=survey.df)
```

Q7&8 Sample Mean: $\bar{X} =  7.498$ 

```{r}
mean(survey.df$Q7and8, data=survey.df)
```

Q9 Sample Mean: $\bar{X} = 6.86$ 

```{r}
mean(survey.df$Q9, data=survey.df)
```

Q10 Sample Mean: $\bar{X} = 7.48$ 

```{r}
mean(survey.df$Q10, data=survey.df)
```

Q11 Sample Mean: $\bar{X} = 3.56$ 

```{r}
mean(survey.df$Q11, data=survey.df)
```

**Boxplots & Density plots for Q4-Q11 columns**

Boxplots & Density plots for Q4
```{r}
ggplot(survey.df, aes(x = Q4, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours devoted to academic work each day during the semester from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q4, xlab="Number of Hours", main="Density Plot of Average hours devoted to academic work each day during the semester from a SRS of Undergraduate Students")
```
Boxplots & Density plots for Q5
```{r}
ggplot(survey.df, aes(x = Q5, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Days") + ylab("") + ggtitle("Boxplot of Average number of days spent playing video games in a week from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q5, xlab="Number of Days", main="Density Plot  of Average number of days spent playing video games in a week from a SRS of Undergraduate Students")
```
Boxplots & Density plots for Q4&5
```{r}
ggplot(survey.df, aes(x = Q4and5, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Days") + ylab("") + ggtitle("Boxplot of Average number of hours spent playing video games in a week from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q4and5, xlab="Number of Days", main="Density Plot  of Average number of hours spent playing video games in a week from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q6
```{r}
ggplot(survey.df, aes(x = Q6, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours spent playing video games in a day from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q6, xlab="Number of Hours", main="Density Plot of Average hours spent playing video games in a day from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q7
```{r}
ggplot(survey.df, aes(x = Q7, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Times") + ylab("") + ggtitle("Boxplot of Average number of times engaged in physical exercise or activities from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q7, xlab="Number of Times", main="Density Plot f Average number of times engaged in physical exercise or activities from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q8
```{r}
ggplot(survey.df, aes(x = Q8, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours of single exercise session from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q8, xlab="Number of Hours", main="Density Plot of Average hours of single exercise session from a SRS of Undergraduate Students")
```
Boxplots & Density plots for Q7&8
```{r}
ggplot(survey.df, aes(x = Q7and8, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours spent engaged in physical exercise or activities per week from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q7and8, xlab="Number of Hours", main="Density Plot of Average hours spent engaged in physical exercise or activities per week from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q9
```{r}
ggplot(survey.df, aes(x = Q9, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours of sleep per day from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q9, xlab="Number of Hours", main="Density Plot of Average hours of sleep per day from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q10
```{r}
ggplot(survey.df, aes(x = Q10, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Hours") + ylab("") + ggtitle("Boxplot of Average hours  spent socializing (face-to-face or virtually) per week from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q10, xlab="Number of Hours", main="Density Plot of Average hours spent socializing (face-to-face or virtually) per week from a SRS of Undergraduate Students")
```

Boxplots & Density plots for Q11
```{r}
ggplot(survey.df, aes(x = Q11, y = "var1")) + geom_boxplot(col="red", fill="blue") + xlab("Number of Courses") + ylab("") + ggtitle("Boxplot of Average number of courses enrolled in this semester (Winter 2023) from a SRS of Undergraduate Students")
#
densityplot(survey.df$Q11, xlab="Number of Courses", main="Density Plot of Average number of courses enrolled in this semester (Winter 2023) from a SRS of Undergraduate Students")
```

**Now we will construct a 95% confidence interval estimate for $\mu$ - the population mean for each numerical survey question (Q4-Q11)**



From this data,
$$
n = 25 \\
N = 53
$$
```{r}
n=25
N = 53
```

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q4**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q4, data=survey.df) #compute various sample statistic on the variable Q4 held in the survey data frame
```

```{r}
meanQ4 = favstats(~Q4, data=survey.df)$mean #assignment of the sample mean 
sdQ4 = favstats(~Q4, data=survey.df)$sd #assignment of the sample standard deviation
meanQ4
sdQ4
```
```{r}
meQ4 = qt(0.975, (n-1))*(sqrt(((sdQ4^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ4)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ4** and **ubQ4** with the following code

```{r}
lbQ4 = meanQ4 - meQ4  #computes the lower bound, assigns this computation to lbQ4
ubQ4 = meanQ4 + meQ4  #computes the upper bound assigned as ubQ4
print(lbQ4)  #displays the lower bound
print(ubQ4)  #displays the upper bound
```
</div>
and
$$
3.364607 \leq \mu \leq 6.075393
$$
From these data, we are 95% confidence that the mean average hours devoted to academic work each day during the semester, including classes and assignments for Undergraduate Students at UofC is somewhere between 3.364607 and 6.075393.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q5**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q5, data=survey.df) #compute various sample statistic on the variable Q5 held in the survey data frame
```

```{r}
meanQ5 = favstats(~Q5, data=survey.df)$mean #assignment of the sample mean 
sdQ5 = favstats(~Q5, data=survey.df)$sd #assignment of the sample standard deviation
meanQ5
sdQ5
```
```{r}
meQ5 = qt(0.975, (n-1))*(sqrt(((sdQ5^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ5)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ5** and **ubQ5** with the following code

```{r}
lbQ5 = meanQ5 - meQ5  #computes the lower bound, assigns this computation to lbQ5
ubQ5 = meanQ5 + meQ5  #computes the upper bound assigned as ubQ5
print(lbQ5)  #displays the lower bound
print(ubQ5)  #displays the upper bound
```
</div>
and
$$
2.379694 \leq \mu \leq 4.900306
$$
From these data, we are 95% confidence that the mean average days where student played video games in a week for Undergraduate Students at UofC is somewhere between  2.379694 and 4.900306.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q4&5**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q4and5, data=survey.df) #compute various sample statistic on the variable Q4and5 held in the survey data frame
```

```{r}
meanQ4and5 = favstats(~Q4and5, data=survey.df)$mean #assignment of the sample mean 
sdQ4and5 = favstats(~Q4and5, data=survey.df)$sd #assignment of the sample standard deviation
meanQ4and5
sdQ4and5
```
```{r}
meQ4and5 = qt(0.975, (n-1))*(sqrt(((sdQ4and5^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ4and5)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ4and5** and **ubQ4and5** with the following code

```{r}
lbQ4and5 = meanQ4and5 - meQ4and5  #computes the lower bound, assigns this computation to lbQ5
ubQ4and5 = meanQ4and5 + meQ4and5  #computes the upper bound assigned as ubQ5
print(lbQ4and5)  #displays the lower bound
print(ubQ4and5)  #displays the upper bound
```
</div>
and
$$
6.047623 \leq \mu \leq 25.83238
$$
From these data, we are 95% confidence that the mean average hours student played video games in a week for Undergraduate Students at UofC is somewhere between 6.047623 and 25.83238.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q6**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q6, data=survey.df) #compute various sample statistic on the variable Q6 held in the survey data frame
```

```{r}
meanQ6 = favstats(~Q6, data=survey.df)$mean #assignment of the sample mean 
sdQ6 = favstats(~Q6, data=survey.df)$sd #assignment of the sample standard deviation
meanQ6
sdQ6
```
```{r}
meQ6 = qt(0.975, (n-1))*(sqrt(((sdQ6^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ6)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ6** and **ubQ6** with the following code

```{r}
lbQ6 = meanQ6 - meQ6  #computes the lower bound, assigns this computation to lbQ6
ubQ6 = meanQ6 + meQ6  #computes the upper bound assigned as ubQ6
print(lbQ6)  #displays the lower bound
print(ubQ6)  #displays the upper bound
```
</div>
and
$$
 1.471878\leq \mu \leq 4.328122
$$
From these data, we are 95% confidence that the mean average hours spent playing video games in a day for Undergraduate Students at UofC is somewhere between  1.471878  and  4.328122.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q7**


Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q7, data=survey.df) #compute various sample statistic on the variable Q7 held in the survey data frame
```

```{r}
meanQ7 = favstats(~Q7, data=survey.df)$mean #assignment of the sample mean 
sdQ7 = favstats(~Q7, data=survey.df)$sd #assignment of the sample standard deviation
meanQ7
sdQ7
```
```{r}
meQ7 = qt(0.975, (n-1))*(sqrt(((sdQ7^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ7)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ7** and **ubQ7** with the following code

```{r}
lbQ7 = meanQ7 - meQ7  #computes the lower bound, assigns this computation to lbQ7
ubQ7 = meanQ7 + meQ7  #computes the upper bound assigned as ubQ7
print(lbQ7)  #displays the lower bound
print(ubQ7)  #displays the upper bound
```
</div>
and
$$
2.386827 \leq \mu \leq 4.229173
$$
From these data, we are 95% confidence that the mean average times student engages in physical exercise or activities per week for Undergraduate Students at UofC is somewhere between   2.386827 and 4.229173.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q8**


Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q8, data=survey.df) #compute various sample statistic on the variable Q8 held in the survey data frame
```

```{r}
meanQ8 = favstats(~Q8, data=survey.df)$mean #assignment of the sample mean 
sdQ8 = favstats(~Q8, data=survey.df)$sd #assignment of the sample standard deviation
meanQ8
sdQ8
```
```{r}
meQ8 = qt(0.975, (n-1))*(sqrt(((sdQ8^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ8)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ8** and **ubQ8** with the following code

```{r}
lbQ8 = meanQ8 - meQ8  #computes the lower bound, assigns this computation to lbQ8
ubQ8 = meanQ8 + meQ8  #computes the upper bound assigned as ubQ8
print(lbQ8)  #displays the lower bound
print(ubQ8)  #displays the upper bound
```
</div>
and
$$
1.115383 \leq \mu \leq  2.524617
$$
From these data, we are 95% confidence that the mean average hours single exercise session lasts for Undergraduate Students at UofC is somewhere between  1.115383 and  2.524617.


**95% confidence interval estimate for $\mu$ - the population mean for survey question Q7and8**


Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q7and8, data=survey.df) #compute various sample statistic on the variable Q7and8 held in the survey data frame
```

```{r}
meanQ7and8 = favstats(~Q7and8, data=survey.df)$mean #assignment of the sample mean 
sdQ7and8 = favstats(~Q7and8, data=survey.df)$sd #assignment of the sample standard deviation
meanQ7and8
sdQ7and8
```
```{r}
meQ7and8 = qt(0.975, (n-1))*(sqrt(((sdQ7and8^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ7and8)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ7and8** and **ubQ7and8** with the following code

```{r}
lbQ7and8 = meanQ7and8 - meQ7and8  #computes the lower bound, assigns this computation to lbQ7and8
ubQ7and8 = meanQ7and8 + meQ7and8  #computes the upper bound assigned as ubQ7and8
print(lbQ7and8)  #displays the lower bound
print(ubQ7and8)  #displays the upper bound
```
</div>
and
$$
 4.173356 \leq \mu \leq 10.82264
$$
From these data, we are 95% confidence that the mean Average hours spent engaged in physical exercise or activities per week from a SRS of Undergraduate Students at UofC is somewhere between 4.173356 and 10.82264.

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q9**


Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q9, data=survey.df) #compute various sample statistic on the variable Q9 held in the survey data frame
```

```{r}
meanQ9 = favstats(~Q9, data=survey.df)$mean #assignment of the sample mean 
sdQ9 = favstats(~Q9, data=survey.df)$sd #assignment of the sample standard deviation
meanQ9
sdQ9
```
```{r}
meQ9 = qt(0.975, (n-1))*(sqrt(((sdQ9^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ9)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ9** and **ubQ9** with the following code

```{r}
lbQ9 = meanQ9 - meQ9  #computes the lower bound, assigns this computation to lbQ9
ubQ9 = meanQ9 + meQ9  #computes the upper bound assigned as ubQ9
print(lbQ9)  #displays the lower bound
print(ubQ9)  #displays the upper bound
```
</div>
and
$$
6.15923 \leq \mu \leq 7.56077
$$
From these data, we are 95% confidence that the mean average hours spent sleeping in a day for Undergraduate Students at UofC is somewhere between 6.15923 and7.56077

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q10**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q10, data=survey.df) #compute various sample statistic on the variable Q9 held in the survey data frame
```

```{r}
meanQ10 = favstats(~Q10, data=survey.df)$mean #assignment of the sample mean 
sdQ10 = favstats(~Q10, data=survey.df)$sd #assignment of the sample standard deviation
meanQ10
sdQ10
```
```{r}
meQ10 = qt(0.975, (n-1))*(sqrt(((sdQ10^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ10)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ10** and **ubQ10** with the following code

```{r}
lbQ10 = meanQ10 - meQ10  #computes the lower bound, assigns this computation to lbQ10
ubQ10 = meanQ10 + meQ10  #computes the upper bound assigned as ubQ10
print(lbQ10)  #displays the lower bound
print(ubQ10)  #displays the upper bound
```
</div>
and
$$
5.534037 \leq \mu \leq 9.425963
$$
From these data, we are 95% confidence that the mean average hours spent socializing (face-to-face or virtually) per week for Undergraduate Students at UofC is somewhere between 5.534037 and 9.425963

**95% confidence interval estimate for $\mu$ - the population mean for survey question Q11**

Now, let's use the `favstats` command to compute various sample statistics:

```{r}
favstats(~Q11, data=survey.df) #compute various sample statistic on the variable Q9 held in the survey data frame
```

```{r}
meanQ11 = favstats(~Q11, data=survey.df)$mean #assignment of the sample mean 
sdQ11 = favstats(~Q11, data=survey.df)$sd #assignment of the sample standard deviation
meanQ11
sdQ11
```
```{r}
meQ11 = qt(0.975, (n-1))*(sqrt(((sdQ11^2)/n)*((N - n)/(n)))) #compute the margin of error of the confidence interval 
print(meQ11)
```

Now we can instruct R to create a "lower bound" and an "upper bound", or **lbQ11** and **ubQ11** with the following code

```{r}
lbQ11 = meanQ11 - meQ11  #computes the lower bound, assigns this computation to lbQ11
ubQ11 = meanQ11 + meQ11  #computes the upper bound assigned as ubQ11
print(lbQ11)  #displays the lower bound
print(ubQ11)  #displays the upper bound
```
</div>
and
$$
2.954165 \leq \mu \leq 4.165835
$$
From these data, we are 95% confidence that the mean average number of courses enrolled in for Undergraduate Students at UofC is somewhere between 2.954165 and 4.165835
